### 2020-03-02 2020.csic5011/homework/homework02.tex
Add files via upload

\lecture{Homework 3. High Dimensional Statistics Models}{Yuan Yao}{Due: Open Date}{March 6, 2019}

@@

\begin{enumerate}
\item {\em Maximum Likelihood Method}: consider $n$ random samples from a multivariate normal distribution, $X_i \in \R^p \sim \NN(\mu,\Sigma)$ with $i=1,\ldots,n$.

\begin{enumerate}
\item Show the log-likelihood function
\[ l_n(\mu,\Sigma) = - \frac{n}{2} \tr(\Sigma^{-1} S_n ) - \frac{n}{2} \log \det(\Sigma) + C, \]
where $S_n = \frac{1}{n}\sum_{i=1}^n (X_i - \mu)(X_i - \mu)^T$, and some constant $C$ does not depend on $\mu$ and $\Sigma$; 
\item Show that $f(X) = \tr(AX^{-1})$ with $A, X\succeq 0$ has a first-order approximation,
\[ f(X+\Delta) \approx f(X) - \tr(X^{-1}A' X^{-1} \Delta ) \]
hence formally $d f(X) / d X = - X^{-1} A X^{-1}$ (note $(I+X)^{-1} \approx I - X$. A typo in previous version missed `-' sign here.);  
\item Show that $g(X) = \log\det(X)$ with $A, X\succeq 0$ has a first-order approximation,
\[ g(X + \Delta) \approx g(X) + \tr(X^{-1} \Delta) \]
hence $d g(X) / d X = X^{-1}$ (note: consider eigenvalues of $X^{-1/2} \Delta X^{-1/2}$); 
\item Use these formal derivatives with respect to positive semi-definite matrix variables to show that the maximum likelihood estimator of $\Sigma$ is 
\[ \hat{\Sigma}^{MLE}_n = S_n. \]
\end{enumerate}
A reference for (b) and (c) can be found in Convex Optimization, by Boyd and Vandenbergh, examples in Appendix A.4.1 and A.4.3:

\url{https://web.stanford.edu/~boyd/cvxbook/bv_cvxbook.pdf}

\item {\em Shrinkage:} Suppose $y\sim \NN(\mu, I_p)$.

\begin{enumerate}
\item Consider the Ridge regression
\[ \min_{\mu} \frac{1}{2}\|y - \mu \|_2^2 +\frac{\lambda}{2} \|\mu\|_2^2. \]
Show that the solution is given by 
\[ \hat{\mu}^{ridge}_i = \frac{1}{1+\lambda} y_i .\]
Compute the risk (mean square error) of this estimator. The risk of MLE is given when $C=I$. 
\item Consider the LASSO problem,
\[ \min_{\mu} \frac{1}{2}\|y - \mu \|_2^2 +\lambda \|\mu\|_1. \]
Show that the solution is given by Soft-Thresholding
\[ \hat{\mu}^{soft}_i = \mu_{soft}( y_i;\lambda) := \sign( y_i ) (|y_i |- \lambda)_+. \]
For the choice $\lambda = \sqrt{2\log p}$, show that the risk is bounded by
\[ \E\|\hat{\mu}^{soft}(y) -\mu\|^2  \leq 1+ (2\log p + 1) \sum_{i=1}^p \min(\mu_i^2,1).\]
Under what conditions on $\mu$, such a risk is smaller than that of MLE?
Note: see Gaussian Estimation by Iain Johnstone, Lemma 2.9 and the reasoning before it.
\item Consider the $l_0$ regularization 
\[ \min_{\mu} \|y - \mu \|_2^2 +\lambda^2 \|\mu\|_0, \]
where $\|\mu\|_0 := \sum_{i=1}^p I(\mu_i \neq 0)$. Show that the solution is given by Hard-Thresholding
\[ \hat{\mu}^{hard}_i = \mu_{hard}( y_i;\lambda) := y_i  I(|y_i|>\lambda).\]
Rewriting $\hat{\mu}^{hard}(y) = (1-g(y))y$, is $g(y)$ weakly differentiable? Why? 
\item Consider the James-Stein Estimator 
\[ \hat{\mu}^{JS}(y) = \left( 1 - \frac{\alpha}{\|y\|^2} \right) y. \]
Show that the risk is 
\[ \E\|\hat{\mu}^{JS}(y) - \mu\|^2 = \E U_\alpha(y) \]
where $U_\alpha(y) = p - (2\alpha(p-2) - \alpha^2) / \|y\|^2$. Find the optimal $\alpha^\ast=\arg\min_\alpha U_\alpha(y)$. Show that for $p>2$, the risk of James-Stein Estimator is smaller than that of MLE for all $\mu\in \R^p$. 
\item In general, an odd monotone unbounded function $\Theta:\R\to\R$ defined by $\Theta_\lambda(t)$ with parameter $\lambda \geq 0$ is called \emph{shrinkage} rule, if it satisfies 
\subitem[shrinkage] $0\leq \Theta_\lambda(|t|) \leq |t|$; 
\subitem[odd] $\Theta_\lambda(-t) = - \Theta_\lambda(t)$;
\subitem[monotone] $\Theta_\lambda(t) \leq \Theta_\lambda(t^\prime)$ for $t\leq t^\prime$;
\subitem[unbounded] $\lim_{t\to \infty} \Theta_\lambda(t)=\infty$. \\
Which rules above are shrinkage rules? 
\end{enumerate}

\item {\em *Necessary Condition for Admissibility of Linear Estimators}. Consider linear estimator for $y\sim \NN(\mu,\sigma^2 I_p)$
\[ \hat{\mu}_C(y) = C y. \]
Show that $\hat{\mu}_C$ is admissible only if
		\begin{enumerate}
			\item $C$ is symmetric;
			\item $0 \le \rho_i(C) \le 1$ (where $\rho_i(C)$ are eigenvalues of $C$);
			\item $\rho_i(C) = 1$ for at most two $i$.
		\end{enumerate}	
		These conditions are satisfied for MLE estimator when $p=1$ and $p=2$.

Reference: Theorem 2.3 in Gaussian Estimation by Iain Johnstone,\\
\url{http://statweb.stanford.edu/~imj/Book100611.pdf}

\item {\em James Stein Estimator for $p=1$:}

From Theorem 3.1 in the lecture notes, we know that MLE $\hat{\mu} = Y$ is admissible when $p=1 \text{ or } 2$. However if we use SURE to calculate the risk of James Stein Estimator,
\[
	R(\hat{\mu}^{\text{JS}},\mu) = \E U(Y) 
	= p - \E_\mu \frac{(p-2)^2}{\lVert Y \rVert^2}
	< p = R(\hat{\mu}^{\text{MLE}},\mu)
\]
it seems that for $p=1$ James Stein Estimator should still has lower risk than MLE for any $\mu$.
 Explain what violates the above calculation for $p=1$.

@@

\begin{enumerate}
\item Find $\lambda$ given $\text{SNR} > \sqrt{\gamma}$.
\item Use your previous answer to explain how the SNR can be estimated from the eigenvalues of the sample covariance matrix.
\item Find the squared correlation between the eigenvector $v$ of the sample covariance matrix (corresponding to the largest eigenvalue $\lambda$) and the ``true" signal component $u$, as a function of the SNR, $p$ and $n$. That is, find $|\langle u,v \rangle|^2$. 
\item Confirm your result using MATLAB or R simulations (e.g. set $u = e$; and choose $\sigma=1$ and $\lambda_0$ in different levels. Compute the largest eigenvalue and its associated eigenvector, with a comparison to the true ones.)
\end{enumerate}

\item {\em Exploring S$\&$P500 Stock Prices:} Take the Standard \& Poor's 500 data: \\
\url{http://math.stanford.edu/~yuany/course/data/snp452-data.mat},\\
which contains the data matrix $X\in \R^{n\times p}$ of $n=1258$ consecutive observation days and $p=452$ daily closing stock prices, and the cell variable ``${\rm stock}$" collects the names, codes, and the affiliated industrial sectors of the 452 stocks. Use Matlab or R for the following exploration. 
\begin{enumerate}
\item Take the logarithmic prices $Y=\log X$; 
\item For each observation time $t\in \{1,\ldots,1257\}$, calculate logarithmic price jumps
\[ \Delta Y_{i,t} = Y_{i,t} - Y_{i,{t-1}}, \ \ \ i\in \{ 1,\ldots, 452 \}; \]
\item Construct the realized covariance matrix $\hat{\Sigma}\in\R^{452\times 452}$ by,
\[ \hat{\Sigma}_{i,j} = \frac{1}{1257} \sum_{\tau =1}^{1257} \Delta Y_{i,\tau} \Delta Y_{j, \tau}; \]
\item Compute the eigenvalues (and eigenvectors) of $\hat{\Sigma}$ and store them in a descending order by $\{\hat{\lambda}_k, k=1,\ldots,p\}$. 
\item \emph{Horn's Parallel Analysis}: the following procedure describes a so-called Parallel Analysis of PCA using random permutations on data. Given the matrix $[\Delta Y_{i,t}]$, apply random permutations $\pi_i: \{1,\ldots,t\} \to \{1,\ldots, t\}$ on each of its rows: $\Delta \tilde{Y}_{i,\pi_i(j)}$ such that 
\[
[\Delta \tilde{Y}_{\pi(i),t}] = \left[
\begin{array}{ccccc}
\Delta Y_{1,1} & \Delta Y_{1,2} & \Delta Y_{1,3} & \ldots & \Delta Y_{1,t} \\
\Delta Y_{2,\pi_2(1)} & \Delta Y_{2,\pi_2(2)} & \Delta Y_{2,\pi_2(3)} & \ldots & \Delta Y_{2,\pi_2(t)} \\
\Delta Y_{3,\pi_3(1)} & \Delta Y_{3,\pi_3(2)} & \Delta Y_{3,\pi_3(3)} & \ldots & \Delta Y_{3,\pi_3(t)} \\
\ldots & \ldots & \ldots & \ldots & \ldots \\
\Delta Y_{n,\pi_n(1)} & \Delta Y_{n,\pi_n(2)} & \Delta Y_{n,\pi_n(3)} & \ldots & \Delta Y_{n,\pi_n(t)} 
\end{array}
\right].
\]
Define $\tilde{\Sigma} = \frac{1}{t} \Delta \tilde{Y} \cdot \Delta \tilde{Y}^T$ as the null covariance matrix. Repeat this for $R$ times and compute the eigenvalues of $\tilde{\Sigma}_r$ for each $1\leq r\leq R$. Evaluate the $p$-value for each estimated eigenvalue $\hat{\lambda}_k$ by $(N_k + 1)/(R+1)$ where $N_k$ is the counts that $\hat{\lambda}_k$ is less than the $k$-th largest eigenvalue of $\tilde{\Sigma}_r$ over $1\leq r \leq R$. Eigenvalues with small $p$-values indicate that they are less likely arising from the spectrum of a randomly permuted matrix and thus considered to be signal. Draw your own conclusion with your observations and analysis on this data. A reference is: Buja and Eyuboglu, "Remarks on Parallel Analysis", Multivariate Behavioral Research, 27(4): 509-540, 1992.
\end{enumerate}

\item *{\em Finite rank perturbations of random symmetric matrices:} Wigner's semi-circle law (proved by Eugene Wigner in 1951) concerns the limiting distribution of the eigenvalues of random symmetric matrices. It states, for example, that the limiting eigenvalue distribution of $n\times n$ symmetric matrices whose entries $w_{ij}$ on and above the diagonal $(i\leq j)$ are i.i.d Gaussians $\mathcal{N}(0,\frac{1}{4n})$ (and the entries below the diagonal are determined by symmetrization, i.e., $w_{ji}=w_{ij}$) is the semi-circle:
    $$p(t) = \frac{2}{\pi} \sqrt{1-t^2}, \quad -1\leq t \leq 1,$$
    where the distribution is supported in the interval $[-1,1]$.
\begin{enumerate}
\item Confirm Wigner's semi-circle law using MATLAB or R simulations (take, e.g., $n=400$).
\item Find the largest eigenvalue of a rank-1 perturbation of a Wigner matrix. That is, find the largest eigenvalue of the matrix $$W + \lambda_0 uu^T,$$ where $W$ is an $n\times n$ random symmetric matrix as above, and $u$ is some deterministic unit-norm vector. Determine the value of $\lambda_0$ for which a phase transition occurs. What is the correlation between the top eigenvector of $W+\lambda_0 uu^T$ and the vector $u$ as a function of $\lambda_0$? Use techniques similar to the ones we used in class for analyzing finite rank perturbations of sample covariance matrices.
\end{enumerate}

>>>>

\lecture{Homework 2. Random Matrix Theory and PCA}{Yuan Yao}{Due: 1.5 weeks}{Feb 26, 2020}

@@

\begin{enumerate}
%\item {\em Maximum Likelihood Method}: consider $n$ random samples from a multivariate normal distribution, $X_i \in \R^p \sim \NN(\mu,\Sigma)$ with $i=1,\ldots,n$.  
%
%\begin{enumerate}
%\item Show the log-likelihood function
%\[ l_n(\mu,\Sigma) = - \frac{n}{2} \tr(\Sigma^{-1} S_n ) - \frac{n}{2} \log \det(\Sigma) + C, \]
%where $S_n = \frac{1}{n}\sum_{i=1}^n (X_i - \mu)(X_i - \mu)^T$, and some constant $C$ does not depend on $\mu$ and $\Sigma$; 
%\item Show that $f(X) = \tr(AX^{-1})$ with $A, X\succeq 0$ has a first-order approximation,
%\[ f(X+\Delta) \approx f(X) - \tr(X^{-1}A' X^{-1} \Delta ) \]
%hence formally $d f(X) / d X = - X^{-1} A X^{-1}$ (note $(I+X)^{-1} \approx I - X$. A typo in previous version missed `-' sign here.);  
%\item Show that $g(X) = \log\det(X)$ with $A, X\succeq 0$ has a first-order approximation,
%\[ g(X + \Delta) \approx g(X) + \tr(X^{-1} \Delta) \]
%hence $d g(X) / d X = X^{-1}$ (note: consider eigenvalues of $X^{-1/2} \Delta X^{-1/2}$); 
%\item Use these formal derivatives with respect to positive semi-definite matrix variables to show that the maximum likelihood estimator of $\Sigma$ is 
%\[ \hat{\Sigma}^{MLE}_n = S_n. \]
%\end{enumerate}
%A reference for (b) and (c) can be found in Convex Optimization, by Boyd and Vandenbergh, examples in Appendix A.4.1 and A.4.3:
%
%\url{https://web.stanford.edu/~boyd/cvxbook/bv_cvxbook.pdf}
%
%
%\item {\em Shrinkage:} Suppose $y\sim \NN(\mu, I_p)$. 
%
%\begin{enumerate}
%\item Consider the Ridge regression
%\[ \min_{\mu} \frac{1}{2}\|y - \mu \|_2^2 +\frac{\lambda}{2} \|\mu\|_2^2. \]
%Show that the solution is given by 
%\[ \hat{\mu}^{ridge}_i = \frac{1}{1+\lambda} y_i .\]
%Compute the risk (mean square error) of this estimator. The risk of MLE is given when $C=I$. 
%\item Consider the LASSO problem,
%\[ \min_{\mu} \frac{1}{2}\|y - \mu \|_2^2 +\lambda \|\mu\|_1. \]
%Show that the solution is given by Soft-Thresholding
%\[ \hat{\mu}^{soft}_i = \mu_{soft}( y_i;\lambda) := \sign( y_i ) (|y_i |- \lambda)_+. \]
%For the choice $\lambda = \sqrt{2\log p}$, show that the risk is bounded by
%\[ \E\|\hat{\mu}^{soft}(y) -\mu\|^2  \leq 1+ (2\log p + 1) \sum_{i=1}^p \min(\mu_i^2,1).\]
%Under what conditions on $\mu$, such a risk is smaller than that of MLE?
%Note: see Gaussian Estimation by Iain Johnstone, Lemma 2.9 and the reasoning before it.
%\item Consider the $l_0$ regularization 
%\[ \min_{\mu} \|y - \mu \|_2^2 +\lambda^2 \|\mu\|_0, \]
%where $\|\mu\|_0 := \sum_{i=1}^p I(\mu_i \neq 0)$. Show that the solution is given by Hard-Thresholding
%\[ \hat{\mu}^{hard}_i = \mu_{hard}( y_i;\lambda) := y_i  I(|y_i|>\lambda).\]
%Rewriting $\hat{\mu}^{hard}(y) = (1-g(y))y$, is $g(y)$ weakly differentiable? Why? 
%\item Consider the James-Stein Estimator 
%\[ \hat{\mu}^{JS}(y) = \left( 1 - \frac{\alpha}{\|y\|^2} \right) y. \]
%Show that the risk is 
%\[ \E\|\hat{\mu}^{JS}(y) - \mu\|^2 = \E U_\alpha(y) \]
%where $U_\alpha(y) = p - (2\alpha(p-2) - \alpha^2) / \|y\|^2$. Find the optimal $\alpha^\ast=\arg\min_\alpha U_\alpha(y)$. Show that for $p>2$, the risk of James-Stein Estimator is smaller than that of MLE for all $\mu\in \R^p$. 
%\item In general, an odd monotone unbounded function $\Theta:\R\to\R$ defined by $\Theta_\lambda(t)$ with parameter $\lambda \geq 0$ is called \emph{shrinkage} rule, if it satisfies 
%\subitem[shrinkage] $0\leq \Theta_\lambda(|t|) \leq |t|$; 
%\subitem[odd] $\Theta_\lambda(-t) = - \Theta_\lambda(t)$;
%\subitem[monotone] $\Theta_\lambda(t) \leq \Theta_\lambda(t^\prime)$ for $t\leq t^\prime$;
%\subitem[unbounded] $\lim_{t\to \infty} \Theta_\lambda(t)=\infty$. \\
%Which rules above are shrinkage rules? 
%\end{enumerate}
%
%\item {\em *Necessary Condition for Admissibility of Linear Estimators}. Consider linear estimator for $y\sim \NN(\mu,\sigma^2 I_p)$
%\[ \hat{\mu}_C(y) = C y. \]
%Show that $\hat{\mu}_C$ is admissible only if
%		\begin{enumerate}
%			\item $C$ is symmetric;
%			\item $0 \le \rho_i(C) \le 1$ (where $\rho_i(C)$ are eigenvalues of $C$);
%			\item $\rho_i(C) = 1$ for at most two $i$.
%		\end{enumerate}	
%		These conditions are satisfied for MLE estimator when $p=1$ and $p=2$. 
%			
%Reference: Theorem 2.3 in Gaussian Estimation by Iain Johnstone,\\
%\url{http://statweb.stanford.edu/~imj/Book100611.pdf}
%
%\item {\em James Stein Estimator for $p=1$:} 
%
%From Theorem 3.1 in the lecture notes, we know that MLE $\hat{\mu} = Y$ is admissible when $p=1 \text{ or } 2$. However if we use SURE to calculate the risk of James Stein Estimator,
%\[
%	R(\hat{\mu}^{\text{JS}},\mu) = \E U(Y) 
%	= p - \E_\mu \frac{(p-2)^2}{\lVert Y \rVert^2}
%	< p = R(\hat{\mu}^{\text{MLE}},\mu)
%\]
%it seems that for $p=1$ James Stein Estimator should still has lower risk than MLE for any $\mu$.
% Explain what violates the above calculation for $p=1$.

@@

\begin{enumerate}
\item Find $\lambda$ given $\text{SNR} > \sqrt{\gamma}$.
\item Use your previous answer to explain how the SNR can be estimated from the eigenvalues of the sample covariance matrix.
\item Find the squared correlation between the eigenvector $v$ of the sample covariance matrix (corresponding to the largest eigenvalue $\lambda$) and the ``true" signal component $u$, as a function of the SNR, $p$ and $n$. That is, find $|\langle u,v \rangle|^2$. 
\item Confirm your result using MATLAB, Python, or R simulations (e.g. set $u = e$; and choose $\sigma=1$ and $\lambda_0$ in different levels. Compute the largest eigenvalue and its associated eigenvector, with a comparison to the true ones.)
\end{enumerate}

\item {\em Exploring S$\&$P500 Stock Prices:} Take the Standard \& Poor's 500 data: \\
%\url{http://math.stanford.edu/~yuany/course/data/snp452-data.mat},\\
\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/snp452-data.mat} \\ 
which contains the data matrix $X\in \R^{n\times p}$ of $n=1258$ consecutive observation days and $p=452$ daily closing stock prices, and the cell variable ``${\rm stock}$" collects the names, codes, and the affiliated industrial sectors of the 452 stocks. Use Matlab, Python, or R for the following exploration. 
\begin{enumerate}
\item Take the logarithmic prices $Y=\log X$; 
\item For each observation time $t\in \{1,\ldots,1257\}$, calculate logarithmic price jumps
\[ \Delta Y_{i,t} = Y_{i,t} - Y_{i,{t-1}}, \ \ \ i\in \{ 1,\ldots, 452 \}; \]
\item Construct the realized covariance matrix $\hat{\Sigma}\in\R^{452\times 452}$ by,
\[ \hat{\Sigma}_{i,j} = \frac{1}{1257} \sum_{\tau =1}^{1257} \Delta Y_{i,\tau} \Delta Y_{j, \tau}; \]
\item Compute the eigenvalues (and eigenvectors) of $\hat{\Sigma}$ and store them in a descending order by $\{\hat{\lambda}_k, k=1,\ldots,p\}$. 
\item \emph{Horn's Parallel Analysis}: the following procedure describes a so-called Parallel Analysis of PCA using random permutations on data. Given the matrix $[\Delta Y_{i,t}]$, apply random permutations $\pi_i: \{1,\ldots,t\} \to \{1,\ldots, t\}$ on each of its rows: $\Delta \tilde{Y}_{i,\pi_i(j)}$ such that 
\[
[\Delta \tilde{Y}_{\pi(i),t}] = \left[
\begin{array}{ccccc}
\Delta Y_{1,1} & \Delta Y_{1,2} & \Delta Y_{1,3} & \ldots & \Delta Y_{1,t} \\
\Delta Y_{2,\pi_2(1)} & \Delta Y_{2,\pi_2(2)} & \Delta Y_{2,\pi_2(3)} & \ldots & \Delta Y_{2,\pi_2(t)} \\
\Delta Y_{3,\pi_3(1)} & \Delta Y_{3,\pi_3(2)} & \Delta Y_{3,\pi_3(3)} & \ldots & \Delta Y_{3,\pi_3(t)} \\
\ldots & \ldots & \ldots & \ldots & \ldots \\
\Delta Y_{n,\pi_n(1)} & \Delta Y_{n,\pi_n(2)} & \Delta Y_{n,\pi_n(3)} & \ldots & \Delta Y_{n,\pi_n(t)} 
\end{array}
\right].
\]
Define $\tilde{\Sigma} = \frac{1}{t} \Delta \tilde{Y} \cdot \Delta \tilde{Y}^T$ as the null covariance matrix. Repeat this for $R$ times and compute the eigenvalues of $\tilde{\Sigma}_r$ for each $1\leq r\leq R$. Evaluate the $p$-value for each estimated eigenvalue $\hat{\lambda}_k$ by $(N_k + 1)/(R+1)$ where $N_k$ is the counts that $\hat{\lambda}_k$ is less than the $k$-th largest eigenvalue of $\tilde{\Sigma}_r$ over $1\leq r \leq R$. Eigenvalues with small $p$-values indicate that they are less likely arising from the spectrum of a randomly permuted matrix and thus considered to be signal. Draw your own conclusion with your observations and analysis on this data. A reference is: Buja and Eyuboglu, "Remarks on Parallel Analysis", Multivariate Behavioral Research, 27(4): 509-540, 1992.
\end{enumerate}

\item *{\em Finite rank perturbations of random symmetric matrices:} Wigner's semi-circle law (proved by Eugene Wigner in 1951) concerns the limiting distribution of the eigenvalues of random symmetric matrices. It states, for example, that the limiting eigenvalue distribution of $n\times n$ symmetric matrices whose entries $w_{ij}$ on and above the diagonal $(i\leq j)$ are i.i.d Gaussians $\mathcal{N}(0,\frac{1}{4n})$ (and the entries below the diagonal are determined by symmetrization, i.e., $w_{ji}=w_{ij}$) is the semi-circle:
    $$p(t) = \frac{2}{\pi} \sqrt{1-t^2}, \quad -1\leq t \leq 1,$$
    where the distribution is supported in the interval $[-1,1]$.
\begin{enumerate}
\item Confirm Wigner's semi-circle law using MATLAB, Python, or R simulations (take, e.g., $n=400$).
\item Find the largest eigenvalue of a rank-1 perturbation of a Wigner matrix. That is, find the largest eigenvalue of the matrix $$W + \lambda_0 uu^T,$$ where $W$ is an $n\times n$ random symmetric matrix as above, and $u$ is some deterministic unit-norm vector. Determine the value of $\lambda_0$ for which a phase transition occurs. What is the correlation between the top eigenvector of $W+\lambda_0 uu^T$ and the vector $u$ as a function of $\lambda_0$? Use techniques similar to the ones we used in class for analyzing finite rank perturbations of sample covariance matrices.
\end{enumerate}
